---
output: github_document
---



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fastfoodworld 

<!-- badges: start -->
<!-- badges: end -->

## Goals

The **goal** of fastfoodworld is to pack all the necessary information that one may need about fast foods into one package. 

* The package comes in with a built-in dataset called **fastfoodinfo** that can loaded up after loading the package library. That data set has nutritional information on various fast food items from various fast food joints like fats, calories, sugar, cholesterol and so on.  

* The package also comes in with 3 handy functions:  
  * **calories_in_Kg()** function - The calories of food items are usually measured in grams. However, on research I found that some places in the world like to measure and read their calories in Kgs for easy understanding. With this function, we can convert a calorie value to kgs so that the section of the world that likes to read their calories in kgs can benefit and understand their food nutrition as well.  
  * **sugar_content() function** - In order to better understand if a fast food item qualified as high sugar item or a low sugar item, this function comes handy. Universally speaking, if sugar content in grams of a single item is more than 8, it is on the higher side of the scale. This function takes  a sugar quantity value in grams as an argument and returns a message explaining if that's high sugar or low sugar.  
  * **cholesterol() function** - This function is related to the shiny app. This function creates a parameterised version of thr cholesterol plot in the Shiny app where the function argument(s) corresponds to the radio button  input. This function lets use chose a restaurant as an argument and then displays the top 5 items from that restaurant with the highest cholesterol quantity.   
* One can also launch an interactive shiny app about the fast food data set from this package using the run_app() function to see statistical summaries in the form of graphics and plots . The user is free to make the choice of inputs to see the respective output on the shiny app.

## Installation

You can install the development version of fastfoodworld from [GitHub](https://github.com/Sanna-Meer) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-Sanna-Meer")
```

The URL for this package is : https://etc5523-2022.github.io/rpkg-Sanna-Meer/

## Example

### This is the inbuilt data set :

```{r data1, echo=TRUE}
library(fastfoodworld)
head(fastfoodinfo, 5)

```

### The shiny app can be run using the following :


```{r shiny, echo=TRUE}

run_app <- function() {
  app_dir <- system.file("myapp", package = "fastfoodworld")
  shiny::runApp(app_dir, display.mode = "normal")
}

```


### The calorie conversion is done using the following function : 

```{r calories, echo=TRUE}
calories_in_Kg <- function(calories) {
  cal <- calories/1000
  return(cal)
}
```


For example : calories_in_Kg(38) returns the value 0.38 and so on.


### The sugar content of an item can be monitored using :

```{r sugar, echo=TRUE}
sugar_content<- function(sugar) {
  if(sugar >= 8)
  print("Beware! High Sugar Quantity!!!")
  else print("Low Sugar Quantity!")
}
```

For example, sugar_content(50) returns the following :
"Beware! High Sugar Quantity!!!"

While sugar_content(6)
 "Low Sugar Quantity!"


### The following function gives the top 5 items with highest cholesterol in the chosen retaurant :

```{r}
cholesterol <- function(restaurant) {
  require(shiny)
  shinyApp(
    ui = fluidPage(
      sidebarLayout(
        sidebarPanel(
                     radioButtons("choice", "Choice:",
                                  c("Mcdonalds",
                                    "Chick Fil-A",
                                    "Sonic",
                                    "Arbys",
                                    "Burger King",
                                    "Subway",
                                    "Taco Bell"
      )
    )
    ),
    mainPanel(textOutput("chol"))

      )
    ),

    server = function(input, output) {
      output$chol <- renderText(
            # MODIFY CODE BELOW: Filter for the selected rest
            filter(restaurant == input$choice) %>%
            print((sort(cholesterol,decreasing=TRUE)))
      )
    }
      )
}
```


One shud render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


All content should be committed and pushed regularly to keep it updated with Github and CRAN.
